Automatic discovery of circuit structure from neural connectomics

### 2013-12-31 docs/paper.tex
reasonably good version before we go hacking it up for submission
updates

%\documentclass{nature}
\documentclass{article}
\usepackage[english,american]{babel}
\usepackage[backend=biber,style=nature]{biblatex}
\usepackage[disable]{todonotes}
\usepackage{subfiles}
\usepackage{grffile}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{fullpage}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{multicol}
\usepackage{csquotes}
\usepackage{pdfpages}
\usepackage{placeins}

@@

@@

\title{Discovering cell type motifs in connectomics data}
\author{Eric Jonas, Konrad Kording}

@@

% \begin{affiliations}
%   \item Something Something
%   \item Something Something
% \end{affiliations}

@@

\begin{figure}[ht!]
  \centering 
  \centerline{\includegraphics[width=5in]{celegans.ai}}
  \caption{Discovering cell types in the \textit{c. elegans}
    connectome. a.) Initial cell connectivity matrix, red are
    (directional) chemical synapses, blue are electrical
    synapses. Point size is proportional to synapse count between
    those cells. b.) Clustered adjacency matrix showing identified
    clusters. c.) Inter-cluster connectivity, showing the position of
    each cell along the body axis as well as the ``true'' cell type --
    both coarse (motor, sensory, and interneuron) as well as fine
    (small text labels). }
  \label{fig:celegans}
\end{figure}

@@

@@

@@

\newpage
\section{Methods }
\subsection{Methods Summary}

@@

\subsection{Microprocessor Netlist annotation}
\label{supp:mos6502netlist}
This is a matrix consisting of the different clusters of nets for 
the registers, with the colors consistent with figure~\ref{fig:mos6502}.

>>>>

%\documentclass{nature}
\documentclass{article}
\usepackage[english,american]{babel}
\usepackage[backend=biber,style=nature]{biblatex}
\usepackage[disable]{todonotes}
\usepackage{grffile}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{fullpage}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{multicol}
\usepackage{csquotes}
\usepackage{pdfpages}
\usepackage{placeins}

@@

%\renewcommand{\includegraphics}[2][]{\fbox{}}

@@

\title{Automatic discovery of circuit structure from neural connectomics}
\author{Eric Jonas$^1$, Konrad Kording$^{2, 3,4}$}

@@

\begin{small}
\begin{enumerate}
  \item Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology, Cambridge, Massachusetts
  \item Department of Physical Medicine and Rehabilitation, Northwestern University and Rehabilitation Institute of Chicago, Chicago, Illinois
  \item Department of Physiology, Northwestern University, Chicago, Illinois
  \item Department of Applied Mathematics, Northwestern University, Chicago, Illinois
\end{enumerate}
\end{small}

@@

@@

\begin{figure}
  \centering 
  \centerline{\includegraphics[width=5in]{celegans.ai}}
  \caption{Discovering cell types in the \textit{c. elegans}
    connectome. a.) Initial cell connectivity matrix, red are
    (directional) chemical synapses, blue are electrical
    synapses. Point size is proportional to synapse count between
    those cells. b.) Clustered adjacency matrix showing identified
    clusters. c.) Inter-cluster connectivity, showing the position of
    each cell along the body axis as well as the ``true'' cell type --
    both coarse (motor, sensory, and interneuron) as well as fine
    (small text labels). }
  \label{fig:celegans}
\end{figure}

@@

\subsection{Methods Summary}

Inference is performed in three steps via composible transition 
kernels -- one for structural, one for per-type parameters, and
one kernel for global parameters and hyperparameters. Details
of data preprocessing, inference parameters, and runtime can
be found in the Methods section.

@@

\begin{itemize}

 \item \textbf{Acknowledgments} We thank Josh Vogelstein for discussions and reading of the manuscript, Finale Doshi-Velez for early discussions on the model, and Erica Peterson, and Jonathan Glidden for extensive manuscript review. 
\item \textbf{Author Contributions} KK and EJ developed model. EJ derived inference, implemented code, tested, and ran experiments. KK and EJ wrote manuscript text and solicited feedback. 
 \item \textbf{Competing Interests} The authors declare that they have no
competing financial interests.
 \item \textbf{Correspondence} Correspondence and requests for materials
should be addressed to E.J.~(email: jonas@mit.edu).
\end{itemize}

\newpage
\section{Methods }

@@

\subsection{Microprocessor Netlist annotation}
\label{supp:mos6502netlist}
This is a matrix consisting of the different clusters of electrical nets for 
the registers, with the colors consistent with figure~\ref{fig:mos6502}.
